---
title: "Biostatistics"
author: "Tanya Deniz Toluay"
date: '2022-12-11'
output:
  html_document:
    theme: cosmo
    code_folding: hide
    toc: true
    toc_float:
      smooth_scroll: false
---

```{r setup, include=FALSE}
# Used libraries 
library(readxl)
library(tidyverse)
library(stats)
library(ggiraphExtra)
```


```{r}

# Import the data including the healthy controls 
Data <- read_excel("C:/deskt/DIR/7th/Desktop/Biostatistics Vasculitis/Data.xlsx", 
                   sheet = "SubSet Data")

# New data frame excluding the healthy controls 
Data2 <- Data[!Data$`Patient Subgroups` == "Healthy Control",]

```



Submitted graphs inspect the quantitative values per subgroup. Please find in the provided document:

* Bar graphs for the quantitative summary visualisation
* Box plots for demonstrating the locality, spread and skewness and box plots with jitter for a better inspection of the diversion of data
* Q-Q plots to investigate the distribution
* Violin plots which are a mix of a box plot and a kernel density plot, show peaks in the data as well as the locality, spread and skewness


The sub-groups include: 

* Patients with skin-limited disease (n=21)
* Patients with renal involvement (n=20)
* Patients with gastrointestinal involvement (n=7)
* Patients with gastrointestinal and renal involvement (n=12)
* Healthy control group (n=22)

The given graphs are both including and excluding the healthy control group for better inspection and they are created regarding sex and the smoking categories. 




## Bar Plots

### Including Healthy Controls 

:::: {style="display: flex;"}

::: {}

#### By Sex

```{r echo=FALSE}

ggplot(Data, aes(Sex, `Adipo (μg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `LBP (μg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data, aes(Sex, `MMP1 ng/ml`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL19 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Kalikrein5 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Leptin (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CXCL5 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")


ggplot(Data, aes(Sex, `Osteopontin (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `IL-15 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CXCL10 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `SERPINA12 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `IL-18 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `FABP-4 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")


```
:::

::: {}


#### By Smoking

```{r echo=FALSE}

ggplot(Data, aes(Smoking, `Adipo (μg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `LBP (μg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data, aes(Smoking, `MMP1 ng/ml`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CCL19 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Kalikrein5 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CCL3 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Leptin (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CXCL5 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")


ggplot(Data, aes(Smoking, `Osteopontin (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `IL-15 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CXCL10 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `ANGPTLA4 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `SERPINA12 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `IL-18 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `FABP-4 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::






### Excluding Healthy Controls 

:::: {style="display: flex;"}

::: {}

#### By Sex

```{r echo=FALSE}

ggplot(Data2, aes(Sex, `Adipo (μg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `LBP (μg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data2, aes(Sex, `MMP1 ng/ml`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL19 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Kalikrein5 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Leptin (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CXCL5 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")


ggplot(Data2, aes(Sex, `Osteopontin (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `IL-15 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CXCL10 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `SERPINA12 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `IL-18 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `FABP-4 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```
:::

::: {}


#### By Smoking

```{r echo=FALSE}

ggplot(Data2, aes(Smoking, `Adipo (μg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `LBP (μg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data2, aes(Smoking, `MMP1 ng/ml`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CCL19 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Kalikrein5 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CCL3 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Leptin (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CXCL5 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")


ggplot(Data2, aes(Smoking, `Osteopontin (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `IL-15 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CXCL10 (pg/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `ANGPTLA4 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `SERPINA12 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `IL-18 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `FABP-4 (ng/ml)`)) +
  geom_bar(stat="identity", fill="black", alpha=0.7) +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::






## Box Plots 

### Including Healthy Controls 



:::: {style="display: flex;"}

::: {}

#### By Sex

```{r echo=FALSE}
ggplot(Data, aes(Sex, `Adipo (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `LBP (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data, aes(Sex, `MMP1 ng/ml`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL19 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Kalikrein5 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Leptin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CXCL5 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Osteopontin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `IL-15 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CXCL10 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `SERPINA12 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `IL-18 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `FABP-4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::: {}

#### Including Jitters

```{r echo=FALSE}
ggplot(Data, aes(Sex, `Adipo (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `LBP (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data, aes(Sex, `MMP1 ng/ml`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL19 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Kalikrein5 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Leptin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CXCL5 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Osteopontin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `IL-15 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CXCL10 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `SERPINA12 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `IL-18 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `FABP-4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```


:::

::::



:::: {style="display: flex;"}

::: {}

#### By Smoking 

```{r echo=FALSE}
ggplot(Data, aes(Smoking, `Adipo (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `LBP (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data, aes(Smoking, `MMP1 ng/ml`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CCL19 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Kalikrein5 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CCL3 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Leptin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CXCL5 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")


ggplot(Data, aes(Smoking, `Osteopontin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `IL-15 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CXCL10 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `SERPINA12 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `IL-18 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `FABP-4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::: {}

#### Including Jitters

```{r echo=FALSE}
ggplot(Data, aes(Smoking, `Adipo (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `LBP (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data, aes(Smoking, `MMP1 ng/ml`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CCL19 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Kalikrein5 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Leptin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CXCL5 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Osteopontin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `IL-15 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CXCL10 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `ANGPTLA4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `SERPINA12 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `IL-18 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `FABP-4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::





### Excluding Healthy Controls


:::: {style="display: flex;"}

::: {}

#### By Sex

```{r echo=FALSE}
ggplot(Data2, aes(Sex, `Adipo (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `LBP (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data2, aes(Sex, `MMP1 ng/ml`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL19 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Kalikrein5 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Leptin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CXCL5 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Osteopontin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `IL-15 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CXCL10 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `SERPINA12 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `IL-18 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `FABP-4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::: {}

#### Including Jitters

```{r echo=FALSE}
ggplot(Data2, aes(Sex, `Adipo (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `LBP (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data2, aes(Sex, `MMP1 ng/ml`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL19 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Kalikrein5 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Leptin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CXCL5 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Osteopontin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `IL-15 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CXCL10 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `SERPINA12 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `IL-18 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `FABP-4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::



:::: {style="display: flex;"}

::: {}

#### By Smoking 

```{r echo=FALSE}
ggplot(Data2, aes(Smoking, `Adipo (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `LBP (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data2, aes(Smoking, `MMP1 ng/ml`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CCL19 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Kalikrein5 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CCL3 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Leptin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CXCL5 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")


ggplot(Data2, aes(Smoking, `Osteopontin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `IL-15 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CXCL10 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `SERPINA12 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `IL-18 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `FABP-4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::: {}

#### Including Jitters

```{r echo=FALSE}
ggplot(Data2, aes(Smoking, `Adipo (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `LBP (μg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data2, aes(Smoking, `MMP1 ng/ml`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CCL19 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Kalikrein5 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Leptin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CXCL5 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Osteopontin (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `IL-15 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CXCL10 (pg/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `ANGPTLA4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `SERPINA12 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `IL-18 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `FABP-4 (ng/ml)`)) +
  geom_boxplot(position = "dodge", fill = "grey66", colour = "black") +
  geom_jitter() +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::



## Q-Q Plots 

### Including Healthy Controls

:::: {style="display: flex;"}

::: {}

#### By Sex 

```{r echo=FALSE, warning= FALSE, message=FALSE, error=FALSE}

ggplot(data = Data, aes(sample=BMI)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("BMI Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`Adipo (μg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`LBP (μg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`MMP1 ng/ml`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`CCL19 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`Kalikrein5 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`CCL3 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`Leptin (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`CXCL5 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`Osteopontin (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`IL-15 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`CXCL10 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`ANGPTLA4 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`SERPINA12 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`IL-18 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`FABP-4 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```


:::

::: {}


#### By Smoking 

```{r echo=FALSE, warning= FALSE, message=FALSE, error=FALSE}

ggplot(data = Data, aes(sample=BMI)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("BMI per Patient SubGroup")

ggplot(data = Data, aes(sample=`Adipo (μg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`LBP (μg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`MMP1 ng/ml`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`CCL19 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`Kalikrein5 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`CCL3 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`Leptin (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`CXCL5 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`Osteopontin (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`IL-15 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`CXCL10 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`ANGPTLA4 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`SERPINA12 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`IL-18 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data, aes(sample=`FABP-4 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::

### Excluding Healthy Controls 

:::: {style="display: flex;"}

::: {}

#### By Sex 

```{r echo=FALSE, warning= FALSE, message=FALSE, error=FALSE}

ggplot(data = Data2, aes(sample=BMI)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("BMI Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`Adipo (μg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`LBP (μg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`MMP1 ng/ml`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`CCL19 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`Kalikrein5 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`CCL3 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`Leptin (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`CXCL5 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`Osteopontin (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`IL-15 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`CXCL10 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`ANGPTLA4 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`SERPINA12 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`IL-18 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`FABP-4 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Sex ~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```


:::

::: {}


#### By Smoking 

```{r echo=FALSE, warning= FALSE, message=FALSE, error=FALSE}

ggplot(data = Data2, aes(sample=BMI)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("BMI per Patient SubGroup")

ggplot(data = Data2, aes(sample=`Adipo (μg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`LBP (μg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`MMP1 ng/ml`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`CCL19 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`Kalikrein5 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`CCL3 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`Leptin (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`CXCL5 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`Osteopontin (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`IL-15 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`CXCL10 (pg/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`ANGPTLA4 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`SERPINA12 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`IL-18 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(data = Data2, aes(sample=`FABP-4 (ng/ml)`)) +
  geom_qq() + 
  geom_qq_line(color="red") + 
  facet_grid(Smoking ~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::


## Violin Plot

### Including Healthy Controls

:::: {style="display: flex;"}

::: {}

#### By Sex

```{r echo=FALSE, warning= FALSE, message=FALSE, error=FALSE}

ggplot(Data, aes(Sex, `Adipo (μg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")


ggplot(Data, aes(Sex, `LBP (μg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data, aes(Sex, `MMP1 ng/ml`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL19 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Kalikrein5 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `Leptin (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CXCL5 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")


ggplot(Data, aes(Sex, `Osteopontin (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `IL-15 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `CXCL10 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `SERPINA12 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `IL-18 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Sex, `FABP-4 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```


:::

::: {}

#### By Smoking

```{r echo=FALSE, warning= FALSE, message=FALSE, error=FALSE}

ggplot(Data, aes(Smoking, `Adipo (μg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")


ggplot(Data, aes(Smoking, `LBP (μg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data, aes(Smoking, `MMP1 ng/ml`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CCL19 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Kalikrein5 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CCL3 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Leptin (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CXCL5 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `Osteopontin (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `IL-15 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `CXCL10 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `ANGPTLA4 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `SERPINA12 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `IL-18 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data, aes(Smoking, `FABP-4 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::

### Excluding Healthy Controls 

:::: {style="display: flex;"}

::: {}

#### By Sex

```{r echo=FALSE, warning= FALSE, message=FALSE, error=FALSE}

ggplot(Data2, aes(Sex, `Adipo (μg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")


ggplot(Data2, aes(Sex, `LBP (μg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data2, aes(Sex, `MMP1 ng/ml`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL19 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Kalikrein5 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CCL3 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `Leptin (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CXCL5 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")


ggplot(Data2, aes(Sex, `Osteopontin (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `IL-15 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `CXCL10 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `ANGPTLA4 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `SERPINA12 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `IL-18 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Sex, `FABP-4 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```


:::

::: {}

#### By Smoking

```{r echo=FALSE, warning= FALSE, message=FALSE, error=FALSE}

ggplot(Data2, aes(Smoking, `Adipo (μg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Adipo (μg/ml) Levels per Patient SubGroup")


ggplot(Data2, aes(Smoking, `LBP (μg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("LBP (μg/ml) Levels per Patient SubGroup")
  
ggplot(Data2, aes(Smoking, `MMP1 ng/ml`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("MMP1 ng/ml Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CCL19 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL19 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Kalikrein5 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Kalikrein5 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CCL3 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CCL3 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Leptin (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Leptin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CXCL5 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL5 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `Osteopontin (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("Osteopontin (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `IL-15 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-15 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `CXCL10 (pg/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("CXCL10 (pg/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `ANGPTLA4 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("ANGPTLA4 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `SERPINA12 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("SERPINA12 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `IL-18 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("IL-18 (ng/ml) Levels per Patient SubGroup")

ggplot(Data2, aes(Smoking, `FABP-4 (ng/ml)`)) +
  geom_violin(fill = "grey66", colour = "black") +
  facet_wrap(~ `Patient Subgroups`) +
  ggtitle("FABP-4 (ng/ml) Levels per Patient SubGroup")

```

:::

::::